% !TEX program = xelatex
\documentclass[10pt,a4paper]{article}
\input{cv_ats_common.tex}
\setmainlanguage{english}
\setotherlanguage{russian}

\begin{document}
\atsbackground
\noindent\makebox[\paperwidth][l]{%
\begin{minipage}[t][\pagecontentheight]{\sidebarwidth}
  \vspace*{0.46cm}
  \hspace*{1.06cm}\begin{minipage}[t][\sidebarinnerheight]{\sidebarinnerwidth}
    \color{softwhite}\RaggedRight
    \SidebarAvatar
    \CVName{Robert\\Bitlev}

    \SidebarSection{Achievements}
    \SidebarRoleTitle{Olympiads in physics\\and informatics}
    \vspace{0.05cm}
    \begin{sidebarbullets}
      \item Winner and prize-winner of the final stage of the All-Russian Olympiad for School Students in Physics.
      \item Gold medalist at the IJSO in 2023 and 2024.
      \item Winner of the ``Technocup'' Olympiad in 2025.
      \item Winner and prize-winner of the regional stage of the All-Russian Olympiad in Informatics.
    \end{sidebarbullets}

    \SidebarSectionSep
    \SidebarSection{Education}
    \EducationEntry{B.Sc. in Computer Science}{St. Petersburg State University}{2025--2029}{St. Petersburg}
    \SidebarEntrySep
    \EducationEntry{Secondary general education}{Lyceum No.\,533}{2016--2025}{GPA: 5.00/5.00}

    \SidebarSectionSep
    \SidebarSection{Languages}
    \LanguageEntry{English}{C1}
    \SidebarEntrySep
    \LanguageEntry{German}{B2--C1}
    \SidebarEntrySep
    \LanguageEntry{Russian}{Native}

    \SidebarSectionSep
    \SidebarSection{Skills}
    \SkillLine{Python \textperiodcentered\ SQL \textperiodcentered\ C++}
    \SidebarEntrySep
    \SkillLine{Machine learning \textperiodcentered\ Data analysis}
    \SidebarEntrySep
    \SkillLine{Algorithms and data structures}
    \SidebarEntrySep
    \SkillLine{Java \textperiodcentered\ HTML/CSS/JavaScript}

    \SidebarSectionSep
    \SidebarSection{Interests}
    \InterestTitle{Applied mathematics\\and computer science}
    \InterestBody{Interested in machine learning, data analysis, algorithmic problem solving, and practical software development.}
    \LeftFooter{}
  \end{minipage}
\end{minipage}%
\begin{minipage}[t][\pagecontentheight]{\mainwidth}
  \vspace*{0.70cm}
  \hspace*{0.66cm}\begin{minipage}[t][\maininnerheight]{\maininnerwidth}
    \TopRole{AI360 Student \textbar\ Mathematics of Machine Learning}
    \vspace{0.09cm}
    \ContactLine{{\MetaLabel{Tel.:}}\ \href{tel:+79215747178}{+7 (921) 574-71-78} \textbar\ {\MetaLabel{Email:}}\ \href{mailto:robertbitlev09@gmail.com}{robertbitlev09@gmail.com}}
    \vspace{0.03cm}
    \ContactLine{{\MetaLabel{GitHub:}}\ \href{https://github.com/robrob09/}{robrob09} \textbar\ {\MetaLabel{Codeforces:}}\ \href{https://codeforces.com/profile/Robrob09}{Robrob09} \textbar\ {\MetaLabel{LinkedIn:}}\ \href{https://www.linkedin.com/in/robert-bitlev-329662377/}{robert-bitlev}}
    \HeaderGap

    \MainSection{Summary}
    \SummaryText{
      AI360 student at the Faculty of Mathematics and Computer Science with a strong interest in machine learning, data analysis, and software development. Completed academic and project-based work involving large-scale data processing, statistical analysis, forecasting, and practical software tools.
    }

    \vspace{0.24cm}
    \MainSection{Projects}
    \MainEntry
      {Resume Builder}
      {Summer 2025}
      {Static web app with layout switcher and PDF export}
      {}
      {\begin{mainbullets}
        \item Built a resume editor from a Figma mockup using HTML, CSS, and vanilla JavaScript, delivering 2 layouts, inline editing, and responsive behavior in a 1-page interface.
        \item Added localStorage persistence and browser-side PDF export, enabling users to edit, save, reset, and export the current version without a backend.
      \end{mainbullets}}

    \MainEntry
      {Assessing support service workload}
      {Spring 2025}
      {Forecasting user requests to technical support}
      {}
      {\begin{mainbullets}
        \item Processed 600k+ support tickets together with product-navigation data, derived user-profile and repeat-contact metrics, and studied how support interactions correlate with DAU growth.
        \item Built a 12-week SARIMAX forecast of weekly workload and a logistic model of request probability to support staffing and workload planning.
      \end{mainbullets}}

    \MainEntry
      {Credit product profiling}
      {Spring 2024}
      {DANO Hackathon, ITMO University}
      {}
      {\begin{mainbullets}
        \item Preprocessed and aggregated client-level data, compared distributions across four lending products, and visualized dependencies with histograms, box plots, scatter plots, and correlation heatmaps.
        \item Identified factors behind product choice and translated the findings into audience-segmentation ideas and recommendations for 3 CRM scenarios: upsell, cross-sell, and downsell.
      \end{mainbullets}}

    \MainEntry
      {Brain Train}
      {2023--2024}
      {Interactive memory trainer on Arduino Nano}
      {}
      {\begin{mainbullets}
        \item Designed an Arduino Nano device with random LED-sequence generation, OLED feedback, hint logic, and button input for short-term memory training.
        \item Integrated 4 Arduino C++ modules - game logic, button handling, display output, and LED patterns - and tuned timing parameters for smoother user interaction.
      \end{mainbullets}}

    \vspace{0.24cm}
    \CoursesSection{Additional Education / Courses}
    \CourseItem{T-Intensive in JavaScript}{T-Education, summer 2025}
    \CourseItem{DANO Hackathon}{ITMO University, spring 2024}
    \CourseItem{School of practical programming and data analysis}{HSE University, 2024--2025}
    \CourseItem{Creative radio electronics}{Academy of Digital Technologies, 2023--2024}
    \CourseItem{Programming school}{Fundamentals of Industrial Programming, 2021--2022}
    \CourseItem{Algorithms and data structures}{Olympiad training, 2021--2022}
    \RightFooter{}
  \end{minipage}
\end{minipage}}
\end{document}
